Transitivity of Subtyping for Intersection Types, Directly

### 2019-06-20 papers/intersection-transitivity.tex
check

\begin{figure}[tbp]
  \[
  \begin{array}{lclr}
    \alpha,\beta & ::= & \TOP \mid c_0 \mid c_1 \mid c_2 \mid \cdots & \text{atoms}\\
    A,B,C,D & ::= & \alpha \mid A → B \mid A ∩ B & \text{types}
  \end{array}
  \]
  \fbox{$A ≤ B$} \\[1ex]
  \begin{tabular}{ll}
    (refl)  & $A ≤ A$ \\[1ex]
    (incl$_L$) & $A ∩ B ≤ A$ \\[1ex]
    (incl$_R$) & $A ∩ B ≤ B$ \\[1ex]
    (glb) & $\inference{A ≤ B & B ≤ C}{A ≤ C}$ \\[1ex]
    ($\TOP_{\mathrm{top}}$) & $A ≤ \TOP$ \\[1ex]
    ($\TOP→$) & $\TOP ≤ A → \TOP$ \\[1ex]
    ($→∩$) & $(A → B) ∩ (A → C) A → (B ∩ C)$ \\[1ex]
    ($→$) & $\inference{A' ≤ A & B ≤ B'}{A → B ≤ A' → B'}$
  \end{tabular}
  \caption{Intersection Types and BCD Subtyping}
  \label{fig:types-subtyping}
\end{figure}

@@

\begin{figure}
  \begin{tabular}{ll}
    (refl$_α$) & $α <: α$ \\[1ex]
    (incl$_L$) & $A ∩ B <: A$ \\[1ex]
    (incl$_R$) & $A ∩ B <: B$ \\[1ex]
    (glb) & $\inference{A <: B & B <: C}{A <: C}$ \\[1ex]
    ($\TOP_{\mathrm{top}}$) & $A <: \TOP$ \\[1ex]
    ($\TOP→$) & $\TOP <: A → \TOP$ \\[1ex]
    ($→$) &$\inference{D ⊆ C & A' <: \dom{D} & \cod{D} <: B' }{C <: A' → B'}$
  \end{tabular}
  \caption{New Subtyping Relation}
  \label{fig:new-subtyping}
\end{figure}

>>>>

\begin{figure}[tbp]
  \[
  \begin{array}{lclr}
    \alpha,\beta & ::= & \TOP \mid c_0 \mid c_1 \mid c_2 \mid \cdots & \text{atoms}\\
    A,B,C,D & ::= & \alpha \mid A → B \mid A ∩ B & \text{types}
  \end{array}
  \]
  \fbox{$A ≤ B$} \\[1ex]
  \begin{tabular}{ll}
    (refl)  & $A ≤ A$ \\[2ex]
    (incl$_L$) & $A ∩ B ≤ A$ \\[2ex]
    (incl$_R$) & $A ∩ B ≤ B$ \\[2ex]
    (glb) & $\inference{C ≤ A & C ≤ B}{C ≤ A ∩ B}$ \\[2ex]
    (trans) & $\inference{A ≤ B & B ≤ C}{A ≤ C}$ \\[2ex]
    ($\TOP_{\mathrm{top}}$) & $A ≤ \TOP$ \\[2ex]
    ($\TOP→$) & $\TOP ≤ A → \TOP$ \\[2ex]
    ($→∩$) & $(A → B) ∩ (A → C) A → (B ∩ C)$ \\[2ex]
    ($→$) & $\inference{A' ≤ A & B ≤ B'}{A → B ≤ A' → B'}$
  \end{tabular}
  \caption{Intersection Types and BCD Subtyping}
  \label{fig:types-subtyping}
\end{figure}

@@

\begin{figure}
  \begin{tabular}{ll}
    (refl$_α$) & $α <: α$ \\[2ex]
    (incl$_L$) & $\inference{A <: C}{A ∩ B <: C}$ \\[2ex]
    (incl$_R$) & $\inference{B <: C} A ∩ B <: C$ \\[2ex]
    (glb) & $\inference{C ≤ A & C ≤ B}{C ≤ A ∩ B}$ \\[2ex]
    ($\TOP_{\mathrm{top}}$) & $A <: \TOP$ \\[2ex]
    ($\TOP→$) & $\TOP <: A → \TOP$ \\[2ex]
    ($→$) &$\inference{D ⊆ C & A' <: \dom{D} & \cod{D} <: B' }{C <: A' → B'}$
  \end{tabular}
  \caption{New Subtyping Relation}
  \label{fig:new-subtyping}
\end{figure}
